\documentclass[9pt]{article}
\setlength{\oddsidemargin}{0in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{-0.65in}
\setlength{\headheight}{0in}
\setlength{\textheight}{9.5in}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\begin{document}
\fontsize{9}{11}\selectfont
\begin{center}
{\bf  {\Large Matthew Brigida}}\\
\hspace*{22pt}561.212.3239 $\bullet$ \href{mailto: matthew.brigida@sunyit.edu}{\color{Blue}{\texttt{matthew.brigida@sunyit.edu}}} $\bullet$
\href{https://github.com/Matt-Brigida}{\color{Blue}{GitHub}} $\bullet$
\href{https://www.youtube.com/channel/UCwekb0vAK-FKaqPF5gfd0eQ?view_as=subscriber}{\color{Blue}{YouTube}}\\
\hspace*{22pt} \href{https://github.com/Matt-Brigida/job_market_materials/raw/master/teaching_phil/teaching_phil.pdf}{\color{Blue}{Statement of Teaching Philosophy}} $\bullet$ \href{https://github.com/Matt-Brigida/job_market_materials/raw/master/Evidence_teaching_effectiveness/Brigida_evidence_teaching_effectiveness.pdf}{\color{Blue}{Evidence of Teaching Effectiveness}} $\bullet$ \href{https://github.com/Matt-Brigida/job_market_materials/raw/master/research_phil/research_phil.pdf}{\color{Blue}{Statement of Research Philosophy}}
\end{center}
EDUCATION:
\begin{itemize}[noitemsep, nolistsep]
\item Ph.D. in Finance, College of Business (AACSB Accredited), Florida Atlantic University, 2009, Dissertation:
``Essays on the Causes and Consequences of Information Leakages Prior to Merger and Acquisition
Announcements''.
\item M.S. Economics, College of Business (AACSB Accredited), Florida Atlantic University, 2004, Thesis: ``Offshoring
and Wage Convergence''.
\item B.B.A., College of Business (AACSB Accredited), Loyola College in Maryland, 2000.
\end{itemize}
\vspace{10pt}
%%
%%
FULL-TIME TEACHING EXPERIENCE\\
{\bf Chair of the Department of Accounting and Finance, Associate Professor of Finance (tenured)}, College of Business (AACSB Accredited), SUNY Polytechnic Institute, 2018--present.
\begin{itemize}[noitemsep, nolistsep]
\item Investments
\item Graduate Investments (online)
\item Financial Problems
\item Intro. to Corporate Finance
\item Financial Analytics
\item Seminar in Finance and Accounting
\end{itemize}
{\bf Associate Professor of Finance (tenured)}, College of Business (AACSB Accredited), Clarion University of Pennsylvania, 2009--2017.
\begin{itemize}[noitemsep, nolistsep]
\item Portfolio Theory
\item Investments
\item Multinational Finance
\item Financial Markets and Institutions
\item Graduate Corporate Finance (online and in-person)
\item Intro. to Corporate Finance
\end{itemize}
\vspace{10pt}
%%
%%
%%
%%
PEER-REVIEWED JOURNAL PUBLICATIONS
\begin{itemize}[noitemsep, nolistsep]
\item Brigida, M. ``The Surprising Irrelevance of Total-Value-Locked on Cryptocurrency Returns {\it Economics Letters} revise and resubmit.
\item Brigida, M. and K. Maceyka ``Time-Variation in Bank Income and Expense Betas'' {\it Managerial Finance} forthcoming.
\item Brigida, M., (2023) ``The Market Value of Decentralization'' {\it Applied Finance Letters}, 12(1), 70 - 76.
\item Pratt, William R., Gustavo A. Barboza, and Matthew Brigida. (2023) ``Leverage and firm value.'' {\it Economic Notes}, Vol. 52, Iss. 2, July: e12218.
\item Brigida, M. (2022).``Credit Default Swaps and Bank Safety''{\it Applied Finance Letters}, 11, 19--27.  \url{https://ojs.aut.ac.nz/applied-finance-letters/article/view/594}
\item Brigida, M. (2020). ``Real-Time Detection of Volatility in Liquidity Provision''. {\it Applied Finance Letters}, 9, 143--156. \url{https://doi.org/10.24135/afl.v9i.268} (\href{https://arxiv.org/abs/2011.10930}{\color{Blue}{arXiv version}}).
\item Brigida, M., 2019, \href{http://www.bankingandfinancereview.com/bfr/index.php/bfr/article/view/1074/180}{\color{Blue}{``The Effect of Bank Regulatory Capital Levels on Loan Types''}}{\it Banking and Finance Review}, Vol 11, No 2.
\item Brigida, M, and W. Pratt, 2019, \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=2848527}{\color{Blue}{High-Frequency Trading and the Weekly Natural Gas Storage Report}}, {\it Studies in Economics and Finance}, Vol. 36 No. 3, pp. 547-566, http://dx.doi.org/10.1108/SEF-03-2018-0092.
\item Brigida, M, 2019, ``Parameter Variation \& the Components of Natural Gas Price Volatility'', {\it Journal of Energy Markets}, Vol. 12, 1 (March), pp. 1--17. DOI: \href{https://doi.org/10.21314/JEM.2018.182}{\color{Blue}{10.21314/JEM.2018.182}}.
\item Brigida, M, and W. Pratt, 2019, \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3125788}{\color{Blue}{``Trade Intensity and Liquidity''}}, {\it Market Microstructure and Liquidity}. Vol 4, No. 1, https://doi.org/10.1142/S2382626619500023.
\item Brigida, M, and W. Pratt 2018, ``Temporal Changes in Capital Structure Determinants”'', {\it Journal of Business and Economic Perspectives}, vol. 46, 1.
\item Brigida, M., 2018, \href{http://www.econpea.org/pub/PER2018Issue25no1.pdf}{\color{Blue}{``Causes of Asymmetric Volatility in Oil Futures''}}, {\it Pennsylvania Economic Review\/}, Vol. 25, Num. 1 (Spring), pp. 78--90.
\item Brigida, M, 2018, ``State Dependence in the Natural Gas Price and Rig Count Relationship'', {\it New York Economic Review}, Vol. 49 (Fall), pp. 63--76.
\item Brigida, M., 2018, ``New Results on the Predictive Value of Crude Oil for US Stock Returns'', {\it Studies in Economics and Finance}, vol. 35, Issue: 1, pp.97--108. https://doi.org/10.1108/SEF-01-2017-0020
\item Pratt, W. R., M. Brigida, and D.O. Jackson, 2017, ``Financing Regimes'', {\it International Review of Accounting, Banking and Finance} 9, 1--36. \href{http://www.irabf.org/publication/Financing Regimes.pdf}{\color{Blue}{http://www.irabf.org/publication/Financing Regimes.pdf}}
\item Brigida, M. and W. Pratt, 2017, ``Fake News'', {\it North American Journal of Economics and Finance\/}, 42C (2017) pp. 564--573, DOI: 10.1016/j.najef.2017.08.012
\item Brigida, M., 2016, ``The Determinants of Regime-Switching in the Natural Gas Crude Oil Cointegrating Relationship'', {\it The Journal of Energy Markets} vol. 9 issue 3, 17--26.
\item Brigida, M., 2014, ``Volatility in Electricity Spread Options'', {\it Pennsylvania Economic Review} vol. 21 issue 1, 1--17.
\item Brigida, M., 2014, ``The Switching Relationship between Natural Gas and Crude Oil Prices'', {\it Energy Economics\/} 43, 48--55.  
\item Brigida, M., J. Madura, and A. Viale, 2013, ``An Information-based Model of Target Stock Price Runup in the Market for Corporate Control'', {\it Quantitative Finance\/}, DOI: 10.1080/14697688.2012.749356.
\item Brigida, M., and J. Madura, 2012, ``Informed Trading Prior to Acquisitions'', {\it Journal of Economics and Business} 64, 185--198.
\item Brigida, M., and J. Madura, 2012, ``Information Leakages Prior to 13D Filings'', {\it Journal of Financial and Economic Practice}, vol. 12, issue 2, 37--52.
\item Brigida, M., 2012, ``The Option in Auto Leases'', {\it Pennsylvania Economic Review} vol. 19 issue 1, 33--44.
\item Brigida, M., 2009, ``A GARCH Analysis of Volatility in Country Indices'', {\it International Journal of Global Management Studies Professional}, vol. 1, issue 3.
\end{itemize}
\vspace{10pt}
%%
%%
WORKING PAPERS
\begin{itemize}[noitemsep, nolistsep]
\item The Determinants of Uninsured Deposits, revise and resubmit at {\it Studies in Economics and Finance} ABDC: B
\item Diversification in Electricity Price and Volume Swaps, revise and resubmit at {\it New York Economic Review} ABDC: C
\item Cross-Sectional Variation in Uninsured Deposits (under review)
\item Hedging Deposit Run Risk Prior to the 2023 Regional Banking Crisis
\item Natural Gas Pipeline Constraints, Market Integration, and Flaring, with Phat Luong
\item Regulatory Capital Levels and Noninterest Income
\item The Determinants of Account Fees at Minority-Owned Depository Institutions
% \item \href{https://docs.google.com/file/d/0B46EsGCAlLnPdmxsT3ZtVGk5Wkk/edit?usp=sharing}{\color{Blue}{Almost Stochastic Dominance: A Penchant for Risk}}, presented at the 2007 FMA conference.
\end{itemize}
\vspace{10pt}
%%
%%
OTHER PUBLICATIONS \& SOFTWARE DEVELOPMENT
\begin{itemize}[noitemsep, nolistsep]
\item Chin W. Yang, Ken Hung, Matthew D. Brigida, and John A. Fox, 2022, 'The Le Chatelier Principle of the Capital Market Equilibrium', \underline{Encyclopedia of Finance}, \url{https://doi.org/10.1007/978-3-030-73443-5_49-1}
\item 39 Arbitrages (2020).
\item Yang, C.W., K. Hung, and M.D. Brigida, 2022, `How Consistent are the Judges of Portfolio Performance?', \underline{The Encyclopedia of Finance}, Published by Springer
\item Barth, J., A. Betru, M. Brigida, and C. Lee, 2018, \href{https://assets1b.milkeninstitute.org/assets/Publication/ResearchReport/PDF/MDIs-A-Market-Overview-7.18.18-FINAL.pdf}{\color{Blue}``Minority-Owned Depository Institutions: A Market Overview''} {\it Milken Institute: Access to Capital Paper Series}
\item \texttt{EIAdata} R package available on \href{http://cran.r-project.org/package=EIAdata}{\color{Blue}{CRAN (stable)}} and \href{https://github.com/Matt-Brigida/EIAdata}{\color{Blue}{Github (development)}}.  The package is an R wrapper for the U.S. Energy Information Administration's API, which allows programmatic access to over a million unique energy related time series.
\item 5MinuteFinance (2016) Created interactive educational materials in R/Shiny to be featured in the Milken Institute site {\color{blue}{5MinuteFinance.org}}. 
\item Yang, C.W., K. Hung, and M.D. Brigida, 2013, `The Le Chatelier Principle of the Capital Market Equilibrium', \underline{The
Encyclopedia of Finance}, Chapter 48, pages 565-568. Published by Springer.
\item Hung, K., C.W. Yang, M.D. Brigida, and D. Means, 2013, `A Critical Evaluation of the Portfolio Performance
Indices Under Rank Transformation', \underline{The Encyclopedia of Finance}, Chapter 21, pages 351-356. Published by
Springer.
\end{itemize}
\vspace{10pt}
%%
%%
AREAS OF INTEREST
\begin{itemize}[noitemsep, nolistsep]
\item {\bf Teaching:} Investments, Portfolio Theory, Financial Institutions, Corporate Finance, and Multinational Finance, Energy Finance.
\item {\bf Research:} High-Frequency Trading, Energy Markets and Finance, Capital Budgeting in the Energy Sector, Time Series Analysis (particularly allowing unobserved variables), Electricity Derivative Pricing (including real option valuation of generation assets), Market Microstructure, Informed Trading.
\end{itemize}
\vspace{10pt}
%%
%%
PRESENTATIONS
\begin{itemize}[noitemsep, nolistsep]
  \item Eastern Finance Association 2017 Annual Meeting (Jacksonville, Florida). ``High-Frequency Trading and Market Efficiency: Evidence from the Weekly Natural Gas Storage Report''.
\item  R/Finance 2016 Annual Meeting, (Chicago, Illinois). ``Community Finance Teaching Resources with R/Shiny''.
\item  International Association for Energy Economics, 2015 North American Conference (Pittsburgh, Pennsylvania), ``The Components of Natural Gas Price Volatility''.
\item  R/Finance 2015 Annual Meeting (Chicago, Illinois), ``Markov-Switching (and some State-Space) Models in R''.
\item Eastern Finance Association Annual Conference, 2014, \href{http://ssrn.com/abstract=2371753}{\color{Blue}{The Switching Relationship between Natural Gas and Crude Oil Prices}}.
\item International Association for Energy Economics, 2013 North American Conference, \href{http://papers.ssrn.com/sol3/papers.cfm?abstract_id=2194215}{\color{Blue}{``The Switching Relationship between Natural Gas and Oil Prices''}}, {\it IAEE/USAEE Best Working Paper for 2012}. 
\item Southern Finance Association, 2010 Annual Meeting, ``Information Leakages Prior to 13D Filings''.
\item Financial Management Association, 2007 Annual Meeting , ``Almost Stochastic Dominance: A Penchant for Risk''.
\end{itemize}
\vspace{10pt}
%%
%%
GRANTS AWARDED
\begin{itemize}[noitemsep, nolistsep]
\item For research on the determinants of Markov-regime switching in the natural gas and crude oil cointegrating relationship. 
\item For research into the determinants of asymmetric volatility in crude oil (WTI) futures. 
\item To reconstruct the portfolio theory course using R code to allow fast theory and strategy testing.
\end{itemize}
\vspace{10pt}
%\clearpage
%%
%%
PROGRAM DEVELOPMENT
\begin{itemize}[noitemsep, nolistsep]
\item PhD Data Analytics, SUNY Polytechnic Institute
\item BS Finance, SUNY Polytechnic Institute
\item MS Data Analytics, SUNY Polytechnic Institute
\item Python in Finance, Milken Institute
\item MBA/Finance, Clarion University
  \begin{itemize}[noitemsep, nolistsep]
    \item Full responsibility for curriculum development.
    \item Program has been approved at all university levels, and plans to admit students in 2015.
    \item Program may be completed fully online.
  \end{itemize}
\item Master in Data Analytics, Clarion University
  \begin{itemize}[noitemsep, nolistsep]
    \item Coordinated the curriculum development.
    \item Program approved July 2015.
    \item Program may be completed fully online.
  \end{itemize}
\end{itemize}
\vspace{10pt}
%%
%%
%%
%%
%%
SERVICE \\
{\bf University-wide:}
\begin{itemize}[noitemsep, nolistsep]
\item Chair Accounting and Finance Department, 2022--present.
\item University-Wide Planning and Budget Committee, 2018--present.
\item Mohawk Valley Mini Maker Faire Steering Committee, 2018.
\item Faculty Senate Technology Subcommittee, 2015 -- 2017.
\item Conduct Board, 2015 -- 2017.
\item Search Committee: Vice President for Finance \& Administration, 2014.
\item University-wide Faculty Development Committee, 2011 -- 2017.
\item Institutional Review Board, 2010 -- 2017. 
\item Clarion University Technology Advisory Council (UTAC), 2013 -- 2015. 
\item APSCUF Finance Department Council Representative, 2014 -- 2017. 
\end{itemize}
{\bf College of Business:}
\begin{itemize}[noitemsep, nolistsep]
\item Coordinator BS in Finance Program, 2020--present.
\item Member of the Leadership Committee (Chairs Council), 2020--present.
\item AACSB Steering Committee, 2018.
\item Dean Search Committee, 2018.
\item AQ/PQ Policy Review Committee, 2009 -- 2010.
\item MBA Program \& Assessment Committee, 2009 -- 2017.
\item Scholarship \& Awards Committee, 2011 -- 2017.
\end{itemize}
{\bf Department:}
\begin{itemize}[noitemsep, nolistsep]
\item Accounting Faculty Search Committee, 2018.
\item Promotion Committee, 2009 -- 2014.
\item Recruitment Committee, 2009 -- 2017.
\item Chair of the Scholarship Committee, 2009 -- 2017.
\item Chair of the Finance Faculty Recruiting Committee, 2010.
\item Finance Department Faculty Advisor to the MBA Program, 2011 -- 2017.
\item Faculty Advisor for finance undergraduate students, 2009 -- 2017.
\item Evaluation Committee, 2014 -- 2017.
\item Tenure Committee, 2014 -- 2017.
\end{itemize}
{\bf Student Organizations}
\begin{itemize}[noitemsep, nolistsep]
\item FMA Club Advisor, 2010 -- 2017.
\end{itemize}
{\bf State System of Higher Education:}
\begin{itemize}[noitemsep, nolistsep]
\item Served on the Proposal Review Committee for the 2013 PASSHE Academic Innovation Conference.
\end{itemize}
{\bf Community:}
\begin{itemize}[noitemsep, nolistsep]
\item Deacon: First Presbyterian Church of Clarion PA.
\item YMCA Soccer Coach.
\item Contribute through documentation writing, and online help, to many Open Source Software initiatives (particularly the Debian Project, Arch Linux, and the R Project for Statistical Computing).
\end{itemize}
{\bf Journals:}
\begin{itemize}[noitemsep, nolistsep]
\item Reviewer for {\it Energy Journal}, {\it Applied Financial Economics}, {\it Financial Review}, {\it Energy Economics}, {\it Managerial Finance} and {\it Economics and Business Letters}.
\end{itemize}
\vspace{10pt}
%%
%%
INDUSTRY EXPERIENCE \\
Algorand Foundation \hfill \hfill 1/2025--present\\
{\bf Chief Economist}
\begin{itemize}[noitemsep, nolistsep]
  \item Created factor pricing models to determine the effect of total-value-locked.
  \item Estimated cryptocurrency risk premia and tested for structural breaks.
\end{itemize}
Huntington Bank \hfill \hfill 10/2022--5/2023\\
{\bf Advisor, Treasury Analytics and Modeling}
\begin{itemize}[noitemsep, nolistsep]
  \item Implemented methods (based on Nelson-Siegel) to predict the term structure of interest rates.
  \item Updated short-rate models for derivative valuation.
\end{itemize}
\vspace{5pt}
Milken Institute, Center for Financial Markets \hfill \hfill 10/2014--7/2021\\
{\bf Financial Education Advisor}
\begin{itemize}[noitemsep, nolistsep]
  \item Securitized equity stakes in various pharmaceutical patents to increase funding available in phase 1 trials.
  \item Created a web application which modeled the decision to purchase a house, as well as other finance related web applications. 
  \item Created interactive presentations in R/Shiny for {\color{Blue}{5MinuteFinance.org}}.
\end{itemize}
\vspace{5pt}
NextEra Energy, NextEra Energy Resources, Juno Beach, FL \hfill  \hfill 2/2009--7/2009\\
{\bf Business Management Analyst/Consultant}
\begin{itemize}[noitemsep, nolistsep]
\item Calculated the real option value of natural gas fired generation assets to assist electricity forward sale decisions and set asset optimization budgets.  The pricing was done by applying Monte Carlo to a spread option where the two underlyings were mean-reverting stochastic processes with price proportional volatility.
\item Determined profitability drivers of wind farms.
\begin{itemize}[noitemsep, nolistsep]
\item Software used: SAP ERP Financials, Oracle databases, R, Excel, Access, some SQL query writing.
\end{itemize}
\end{itemize}
\vspace{5pt}
Florida Atlantic University, Boca Raton, FL \hfill  \hfill 1/2006--5/2009\\
{\bf Finance Instructor \& Research Assistant}
\begin{itemize}[noitemsep, nolistsep]
\item Modeled time series and volatility (including ARCH/GARCH models with endogenous regime-switching and a GJR leverage effect), and implemented conditional autoregressive Value-at-Risk .
\item Priced options with Stochastic Volatility models (including Heston calibration).
\end{itemize}
\vspace{5pt}
World Omni Financial Corp. (Southeast Toyota Finance), Deerfield Beach, FL \hfill  \hfill 12/2004--1/2006\\
{\bf Senior Modeling Analyst}
\begin{itemize}[noitemsep, nolistsep]
\item Created a nested Logit model to estimate delinquency and default probabilities for multi-billion dollar portfolios of auto loans and leases.
\item Priced the option sold in our auto leases.
\begin{itemize}[noitemsep, nolistsep]
\item Software used:  SAS, Excel, Access, SQL query writing.
\end{itemize}
\end{itemize}
\vspace{10pt}

TEACHING RELATED PROJECTS
\begin{itemize}[noitemsep, nolistsep]
\item Created a MySQL database relating hourly PJM electricity prices and FTR auction values by network node.
\item Created a PostgreSQL database of all Fannie Mae and Freddie Mac loan-level files.
\item Created an operating system for students to run as a live CD. This enables students to have all programs they need for my courses (and quantitative finance in general) available on any computer anywhere.
\item Supervised student research papers.
\end{itemize}
\vspace{10pt}

\noindent OTHER TEACHING EXPERIENCE\\
{\bf Finance Instructor}, College of Business (AACSB Accredited), Florida Atlantic University.
\begin{itemize}[noitemsep, nolistsep]
\item Principles of Financial Management, Spring 2008, Fall 2008, Spring 2009.
\end{itemize}
{\bf Mathematics Instructor}, College of Arts and Sciences, Florida Atlantic University.
\begin{itemize}[noitemsep, nolistsep]
\item Introductory Statistics (3 sections, each 2 credit hours), Fall 2004.
\end{itemize}
{\bf Economics Teaching Assistant}, College of Business (AACSB Accredited), Florida Atlantic University.
\begin{itemize}[noitemsep, nolistsep]
\item Advanced Econometrics, Advanced Mathematical Economics, Advanced Micro \& Macro, 2003 - 2004.
\end{itemize}
\vspace{10pt}
TECHNICAL SKILLS:
\begin{itemize}[noitemsep, nolistsep]
\item Software: Python, Pytorch, R, SAS, SQL (MySQL), QRM, Advanced Excel, Access, Word, SAP ERP, C++, UNIX/Linux, \LaTeX, Emacs Lisp, C. 
\item Databases/Interfaces: Oracle, WRDS, CRSP, Datastream, SDC Platinum, Compustat, TAQ data.
\item Operating Systems: GNU/Linux, Windows.
\end{itemize}
\vspace{10pt}
%%
%%
MEMBERSHIPS
\begin{itemize}[noitemsep, nolistsep]
\item United States Association for Energy Economics (USAEE)
\item Phi Kappa Phi
\item Omicron Delta Epsilon, International Honor Society in Economics.
\item Financial Management Association (FMA).
\item Eastern Finance Association (EFA).
\end{itemize}
\vspace{15pt}
%%
%%
% \clearpage
% \noindent REFERENCES \\
% \\
% Chin Yang \\
% Professor of Economics \\
% Clarion University of Pennsylvania \\
% yang@clarion.edu \\
% 814.393.2609 \\
% \\
% Gustavo Barboza \\
% Professor of Administrative Science \\
% Clarion University of Pennsylvania \\
% gbarboza@clarion.edu \\
% 814.393.2053 \\
% \\
% William Pratt \\
% Associate Professor of Finance \\
% Clarion University of Pennsylvania \\
% wpratt@clarion.edu \\
% 805.390.7163
%% Jeff Madura \\
%% SunTrust Bank Professor of Finance (retired) \\
%% Florida Atlantic University \\
%% jeffmadura@bellsouth.net 


%PUBLICATIONS:
%\begin{itemize}[noitemsep, nolistsep]
%\item \href{https://docs.google.com/file/d/0B46EsGCAlLnPc3E1MzIzMmZyQjQ/edit?usp=sharing}{\color{Blue}{An Information Based Model of Target Stock Price Runup in the Market for Corporate Control}}, {\it Quantitative Finance}, 2013.
%\item \href{https://docs.google.com/open?id=0B46EsGCAlLnPOTQ3ZGE3NjQtOWI3ZC00ZWNlLThhYjQtYzA4NWM2Mzg3NDZm}{\color{Blue}{Sources of Target Stock Price Runup Prior to Acquisitions}}, {\it Journal of Economics and Business}, 2012.
%\item \href{https://sites.google.com/site/completemarkets/Home/publications/Manuscript_InfoLeakage13DFiling.pdf?attredirects=0&d=1}{\color{Blue}{Information Leakages Prior to 13D Filings}}, {\it Journal of Financial and Economic Practice}, 2012.
%\item \href{https://docs.google.com/open?id=0B46EsGCAlLnPZ3h5Y2prZEdSaGM}{\color{Blue}{The Option in Auto Leases}}, {\it Pennsylvania Economic Review}, 2012.
%\item \href{https://sites.google.com/site/completemarkets/Home/publications/BrigidaGARCHfinalmanuscript.pdf?attredirects=0&d=1}{\color{Blue}{A GARCH Analysis of the Volatility in Country Indices}}, {\it Intl. Journal of Global Management Studies Professional}, 2009.
%\end{itemize}
\end{document}

